# DIYDDICurator

## Description

The DIYDDICurator is a graphic user interface to the `rddi` package. It is a shiny app designed to streamline metadata generation for research data sharing. It allows the user to input project metadata and generate a valid Data Documentation Initiative Codebook (DDI 2.5) to describe the study and data collected.

DDI elements and their attributes are listed in various tabs and described using a `handsontable` (https://handsontable.com/). By right clicking on the table users can add or delete rows. A human readable README, the DDI Codebook and the data is available for export in the Export navigation menu. 

## Installation

It is recommended to use the development version of rddi from Github

```{r}
# install.packages("devtools")
devtools::install_github("nyuglobalties/rddi")
```

DIYDDICurator installation

```{r}

devtools::install_github("nyuglobalties/DIYDDICurator")

```

## Launch DIY DDI Curator

```{r}
library(DIYDDICurator)
curator()

# or
DIYDDICurator:curator()
```


